% !TeX spellcheck = en_US
% !TeX root = main.tex

\chapter{Conclusion}
% Summarise and conclude your Design Report
% In short, how has your website been successful in responding to the brief?
To conclude, the website created provides a platform to learn and test their skills at \gls{git}. It follows all the goals set out in the early design phase (Section~\ref{sec:goals}), and is enjoyable with a good user experience. The site does seem to present content which can be difficult for people to understand, however people with some programming background (as a requirement of the target audience) seem to really flow smoothly through the content and have a reasonably solid understanding afterwards. The addition of the quiz at the end of the journey really helps to tie in the content learnt and cement the knowledge.

\section{Course Reflection}
% How has your learning strategy changed since the start of the course?
% If you had the change to restart, how would you approach your learning differently?
Given a chance to start the course content again I would first of all focus more on the design side of the course and really get a solid design plan and have it tested more before beginning development. Seen as I already have a solid background in the practical content it would be more beneficial to provide more design insights. I also think I would focus more on the individual components of the website and less on the overall content, starting by looking at a really basic component toolkit which is then extended to the entire website.\\\\
I would also have liked to investigate topics that might be easier for people in the course to understand. I am passionate about \gls{git}, however when it came time to user testing on a lot of the content, a lot of the people were not interested to invest the amount of time required to properly learn the content and led to results which were less than favourable. However given people with more programming knowledge and a proper willingness to learn \gls{git}, they enjoyed the site and thought it was perfect for them. I would have liked to pick a topic which is much more suitable to both audiences.